The value of intermediation

### 2022-09-14 src/presentation/presentation.qmd
Add literature review

>>>>

## Related literature

 - Shapley-value as a bargaining outcome
   - [@gul1989bargaining; @winter1994demand; @hart1996bargaining; @stole1996intra]
 - Cooperative bargaining in IO models
   - [@billera1978internal; @hart1990property; @levy1997individual; @segal2003collusion; @inderst2003bargaining; @montez2007downstream]
 - Values of oceanic games
   - [@hart1973values; @fogelman1980asymptotic]
 - Hybrid platforms
   - [@anderson2021hybrid; @hagiu2022should]
